\input{setup/preamble.tex}
\input{setup/macros.tex}
% !TEX root =main.tex
\begin{document}
    %%% TItle %%%
    \tcbset{colframe=title,colback=title,arc=0mm}
    \begin{tcolorbox}
        \begin{minipage}{0.65\textwidth} % Name and Contact Info
            \name{Mohammad Choupan}{Full stack developer} % Name and Profession
            \vspace{2em}
            \email{mohamadchoupan80@gmail.com} $\cdot$
            \phone{+98 9126196168} \par \vspace{0.5em}
            \address{Tehran, Iran} $\cdot$
            \github{https://github.com/mohamadch91}{mohamadch91} $\cdot$
            \linkedin {https://www.linkedin.com/in/mohamad-choupan-629959245/}{Mohamad Choupan}
        \end{minipage}
        
    \end{tcolorbox}

    %%% Sections %%%
    \vspace*{-1em}
    \tcbset{colframe=white,colback=white,arc=0mm, height=0.8\textheight}
    \begin{tcolorbox}
        \vspace*{-0.5em}
        \begin{minipage}[t]{0.2\textwidth} % Side Panel (e.g. Skills, Links, Languages, etc.)
            \begin{tcolorbox}[height=0.8\textheight, grow to left by=0.6cm,colback=backdrop,colframe=backdrop,arc=0mm]

                % Skills, the skill level is drawn as bars, input: skill name and an array starting from 0 and ending before 4
                \subsection{Skills}

                    \skill{Python}{0, 1, 2, 3,4}
                    \skill{Git}{0, 1, 2,3,4}
                    \skill{Linux}{0, 1, 2, 3,4}
                    \skill{ReactJS}{0, 1, 2, 3, 4}
                    \skill{Django,DRF}{0, 1, 2, 3, 4}
                    \skill{Docker,kubernetes}{0, 1, 2, 3}
                    

                \subsection{Languages}

                    \lan{Persian}{0, 1, 2, 3,4}
                    \lan{Turkish}{0, 1, 2, 3,4}
                    \lan{English}{0, 1, 2, 3}
                  \subsection{Interests}

                    \edu{Machine Learning}
                    \edu{Computer vision}
                    \edu{Open source}
                    
                    
               
            \end{tcolorbox}
        \end{minipage}
        \begin{minipage}[t]{0.75\textwidth} % Main Panel (e.g. Education, Work Experience)
            \begin{tcolorbox}[grow to right by=0.75cm,height=0.8\textheight,colframe=white,colback=white]

                % Profile Section
                \section*{Profile}
                Graduated from Amirkabir University of Technology with a degree in Computer Engineering. A full-stack developer with over 4 years of experience, skilled in building web applications from the ground up. Proficient in agile methodologies and comfortable working in fast-paced environments.
                \vspace{-1.5em}
                % Work Experience
                   \section*{Work Experience}
                    \pubw{Full stack developer }{Feb 2021 - Oct 2021}{Puzzle studio}{
                    Puzzle Studio is a company that provides live stream server solutions and web development services for its customers. I am responsible for maintaining their live stream servers as well as developing websites for their clients.
                    }
                    
                    \pubw{Freelancing}{Oct 2021 - Feb 2024}{ Remote}{
                   Freelancing as a full-stack developer for major organizations such as WHO, WVSSM, Odyssey, Hadaf School, Baham Store and POD
                    }
                    
                    \pubw{Front-end Team Lead }{Feb 2024 - Aug 2024}{ Goldiran Asayesh}{
                        Goldiran Asayesh is a company that provides insurance services. I am responsible for leading a team of three front-end developers to create a new website for the company and manage existing websites, such as\link{https://goldiranasayesh.com/}{Goldiran Asayesh}
                        \link{https://tech.kardoon.ir/}{Kardoon}
                        \link{https://inzi.ir/}{Inzi(Not completed)}.
                        Additionally, I handle DevOps tasks, including CI/CD, Docker, and web server management.
                    }
                \vspace{-1.5em}

                \section*{Projects}
                \pub{LandoLet}{May 2022 - June 2022}{Odessey}{
                    LandoLet is a mobile app for renting an apartment in uk,
                    I'm using Django-DRF to develop the back end of this mobile app 
                }{https://github.com/mohamadch91/LandoLet-app-backend}

                    \pub{Inventory and gap analysis system}{June 2022 - Dec 2022}{Full stack Developer}{
                        The inventory system is a system for managing items and facilities that WHO gave to countries.
                        I am designing a full website and mobile app for this app using ReactJS and Django this project is deployed in many countries as Ukraine, Timor-Leste and ...
                    }{https://github.com/mohamadch91/inventory}

                    \pub{POD app}{Aug 2023 - present}{Full stack Developer}{
                        Pod App is a petroleum marketplace where users can buy and sell petroleum products. I am responsible for developing both the website and the admin Panel app for this project using ReactJS and Django. The app is currently still under development.
                    }{http://app-pod.com/}
                    \pub{Baham Store}{May 2024 - Sep 2024}{Back end devloper}{
                        Baham Store is an online platform that offers a wide range of products. I am responsible for developing the back-end of the website using Django and Django Rest Framework (DRF). Additionally, I handle DevOps tasks and manage the mail server development.}{https://bahamstore.ir}
                
                    
                    
                    
                   
                % Education
                
            

                % Publications
              
            \end{tcolorbox}
        \end{minipage}
    \end{tcolorbox}
    
\end{document}