\documentclass[11pt,a4paper,sans]{moderncv}
% Possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape'), and font family ('sans' and 'roman')

%----------------------------------------------------------------------------------------
% COLORS
%----------------------------------------------------------------------
\usepackage{xcolor}
% \usepackage{titlesec}/
% Main color
% \definecolor{maincol}{RGB}{255,150,0}
% \titlespacing{\section}{0pt}{\parskip}{-\parskip}
% Secondary colors
% \definecolor{secondcol}{RGB}{0,178,255}
\definecolor{thirdcol}{HTML}{3873B2}
% \definecolor{fourthcol}{RGB}{0,100,160}
% \definecolor{fifthcol}{RGB}{0,120,200}
% \definecolor{sixthcol}{RGB}{0,80,130}
\definecolor{color1}{HTML}{3873B2}
% Background color
% \definecolor{bgcol}{RGB}{255,255,255}

% Text color
% \definecolor{textcol}{RGB}{0,50,80}

% Section color
% \definecolor{sectcol}{RGB}{56,115,178}

\usepackage{mathpazo}
\usepackage{tikz}
\usetikzlibrary{arrows}

% Moderncv themes
\moderncvstyle{banking} % Style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % Color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', and 'black'
%\renewcommand{\familydefault}{\sfdefault} % To set the default font; use '\sfdefault' for the default sans-serif font, '\rmdefault' for the default roman one, or any TeX font name
\nopagenumbers{} % Uncomment to suppress automatic page numbering for CVs longer than one page

% Character encoding
\usepackage[utf8]{inputenc}
\usepackage{pdfpages}

% If you are not using xelatex or lualatex, replace with the encoding you are using
%\usepackage{CJKutf8} % If you need to use CJK to typeset your resume in Chinese, Japanese, or Korean
\usepackage{multicol}

% Adjust the page margins
\usepackage[scale=0.8,top=0.5cm,bottom=0.1cm]{geometry}
% \usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm} % If you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. Be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage{xpatch}
\xpatchcmd\cventry{,}{}{}{}
\makeatletter
\xpatchcmd\makehead
   {\titlestyle{~|~\@title}}%
   {\newline\newline\titlestyle{\@title}
   }%
   {}{}
\makeatother
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=thirdcol,
}


\vspace{7mm}
% Personal data

\name{}{\hspace{10mm}\textcolor{black}{Mohammad Choupan}}
\title{Full Stack Engineer} % Optional, remove/comment the line if not wanted

% \name{\textcolor{black}{Mohammad}}{\textcolor{black}{Choupan}}


% \address{70 Absolute Ave.}{L4Z 0A4 Mississauga}{Canada} % Optional, remove/comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
% \vspace*{7mm}
% \address % \address{pariyamd.github.io}
\phone[mobile]{+39 3520 119 670}
% \title{\normalfont}
% Optional, remove/comment the line if not wanted
% \phone[fixed]{+2~(345)~678~901} % Optional, remove/comment the line if not wanted
% \phone[fax]{+3~(456)~789~012} % Optional, remove/comment the line if not wanted
\email{mohamadchoupan80@gmail.com}
% Optional, remove/comment the line if not needed
\social[github]{mohamadch91}
% \social[linkedin]{mohammad-choupan-629959245}
% \photo[80pt][0.1pt]{pariya.png} % \date{2000-07-18}
%----------------------------------------------------------------------------------
% Content
%----------------------------------------------------------------------------------

\begin{document}
% \vspace {0mm}
\makecvtitle

\vspace {-2em}

\section{Profile}
\vspace{-1mm}
MSc student in Artificial Intelligence at the University of Bologna and Full Stack Engineer with 5+ years of experience building and operating web applications. Specializing in Python, Django, React, and Next.js, with a focus on scalable APIs, responsive UI development, and robust back-end systems. Experienced in Agile teams and fast-paced environments.
%------------------------------

 % \setlength{\tabcolsep}{1pt}.
% \section{Research Interests}
% \vspace{-4mm}
% \begin{multicols}{3}
%     \begin{itemize}
%     \item Computer Vision
%     \item Panoptic Segmentation
%     \item Point Cloud Classification
% \vspace{-4mm}
    
%     \end{itemize}
% \vspace{-4mm}
    
% \end{multicols}


\section{Technical Skills}
\begin{itemize}
    \item \textbf{Languages:} Python, JavaScript (ES6+), TypeScript, HTML5, CSS3, SQL, Bash
    \item \textbf{Front-End:} React, Next.js, React Native, Redux Toolkit, Amazon Cloudscape
    \item \textbf{Back-End:} Django, Django REST Framework (DRF), REST APIs, Celery, gRPC
    \item \textbf{Databases \& Caching:} PostgreSQL, MySQL, Redis, RabbitMQ
    \item \textbf{Testing/Tooling:} Pytest, Jest, React Testing Library, Postman, Swagger/OpenAPI
    \item \textbf{GitOps / DevOps:} Git, GitLab CI/CD, GitHub Actions, Docker, Kubernetes, Helm
\end{itemize}




\section{Work Experience}
\vspace{1mm}

\cventry{2025 -- 2026}{Front-End Team Lead \& DevOps Engineer}{Goldiran Asayesh}{Tehran, Iran}{}{
\vspace{1mm}
Goldiran Asayesh is an insurance provider for home appliances in Iran, with three product managers and field technicians handling repair and sales operations.
\begin{itemize}
\item Led a team of 3 front-end developers to launch a new customer-facing website and manage \textbf{4} products: \href{https://goldiranasayesh.com/}{Goldiran Asayesh}, \href{https://tech.kardoon.ir/}{Kardoon}, \href{https://inzi.ir/}{Inzi}, and \href{https://nexoland.ir}{Nexoland}.
\item Migrated from manual builds to automated Jenkins/GitLab CI/CD pipelines (GitOps), making builds \textbf{2$\times$ faster} and cutting final bundle size by \textbf{40\%}.
\item Directed front-end execution end-to-end: UI/component architecture (React), code reviews, and cross-functional coordination with product and back-end teams.
\item Executed Docker-based build and deployment workflows, and set up centralized logging (Elasticsearch) and monitoring (Prometheus, Grafana) to increase service visibility.
\end{itemize}}
\vspace{1mm}

\vspace{1mm}
\cventry{2024 -- 2025}{Full Stack Developer}{OpenSecurity (OpenGovern)}{Remote}{}{
\vspace{1mm}
OpenSecurity (OpenGovern) is a US-based \textbf{open-source} startup building a compliance and security platform for containerized and cloud environments. \href{https://github.com/opengovern/}{GitHub}
\begin{itemize}
\item Built and maintained full-stack flows (Python APIs, React/Amazon Cloudscape UI), collaborating with distributed engineers to deliver compliance dashboards.
\item Created a Python package to manage an AI/LLM pipeline (prompt orchestration, tool execution, structured outputs) for product automation.
\item Amplified overall application performance by \textbf{60\%} through base library replacements, back-end request/response tuning, and front-end rendering optimizations.
\item Applied Kubernetes packaging via a Helm chart and enforced CI/CD release automation; reduced installation time to under 2 minutes.
\item Enhanced Steampipe usability by enabling offline SQL querying on cached datasets (500+ tables) for restricted-network environments.
\item Led delivery of 15+ integrations/plugins across GitHub, Kubernetes, and major cloud providers (AWS, Azure, GCP).
\end{itemize}}
\vspace{1mm}

\cventry{2024 -- 2024}{Full Stack Engineer (Freelance Project)}{Baham Store}{Tehran, Iran}{}{
\href{https://bahamstore.ir}{Website}
\begin{itemize}
    \item Created the e-commerce platform end-to-end, building the back end with Python/Django and the mobile-first front end with React for a robust shopping experience.
    \item Managed a catalog of \textbf{10K+ products} using Celery for asynchronous jobs, caching for DB optimization, and responsive React UI components.
    \item Increased sales by \textbf{40\%} and achieved \textbf{2$\times$} during Black Friday by optimizing back-end performance and streamlining checkout UX.
\end{itemize}}

\newpage
\clearpage

\cventry{2023 -- 2024}{Full Stack Developer}{INVGAP (Inventory \& Gap Analysis), World Health Organization (WHO)}{Remote}{}{
\vspace{1mm}
INVGAP is a WHO program for monitoring vaccine inventory and identifying supply gaps across multiple countries. \href{https://aze.invgap.org}{Inventory Gap Analysis System}
\begin{itemize}
\item Developed the back-end data model (Django, \textbf{40+ database tables}) and designed the complex hierarchical (tree) front-end UI using React.js and TypeScript.
\item Released a companion React Native mobile app to the App Store to expand access for field workers: \href{https://apps.apple.com/de/app/inventory-and-gap-analysis/id6447693397}{Inventory and Gap Analysis}.
\item Processed large data imports (\textbf{Excel files up to 30\,MB}), applying validation, batching, and safe transaction handling.
\item Maintained high-throughput APIs and coordinated deployment readiness (load balancing, scaling), ensuring reliable operation for \textbf{1000+ concurrent users} across \textbf{26+ countries}.
\end{itemize}}
\cventry{2021 -- 2023}{Full Stack Developer (Freelance)}{Freelancer}{Tehran, Iran}{}{
\begin{itemize}
    \item \textbf{POD App (petroleum marketplace).} \href{https://pod-app.com}{Website}
    \begin{itemize}
        \item Built the customer-facing web application (React) and comprehensive back-end services (Python/Django) supporting marketplace and administration workflows.
        \item Applied \textbf{gRPC} for microservice-to-microservice communication and \textbf{RabbitMQ/Celery} for reliable asynchronous task processing.
    \end{itemize}
    \vspace{1mm}
    \item \textbf{LandoLet (rental platform).}
    \begin{itemize}
        \item Created responsive UI screens (search, listings, booking flows) and built Python/Django APIs securely linking client logic with relational data models.
        \item Enforced rigorous authentication/authorization and systemized testing to ensure a predictable user journey.
    \end{itemize}
    \vspace{1mm}
    \item \textbf{Cloud Drive (internal tool).}
    \begin{itemize}
        \item Created a lightweight, scalable cloud-drive SPA and back-end file service using Django, implementing chunked uploads and background processing.
        \item Ensured simple UX and fast metadata retrieval via optimized indexed queries and caching.
    \end{itemize}
\end{itemize}}





\section{Education}

\cventry{2025 -- Present}{MSc in Artificial Intelligence}{University of Bologna, Italy}{}{}{
\begin{itemize}
    \item GPA: 30/30
\end{itemize}}

\cventry{2020 -- 2024}{Bachelor's Degree}{Amirkabir University of Technology, Tehran, Iran}{Computer Engineering}{}{\begin{itemize}
    \item GPA: 3.7/4
    \item GPA Over the Last Two Years: 3.83/4
\end{itemize}}

% \cventry{2016 -- 2019}{Diploma}{Atomic Energy High School, Tehran, Iran}{Mathematics and Physics Discipline}{}{}
% \vspace*{0.5em}
% \section{BSc Thesis}

% \cventry{August 2023 - June 2024}{Assessment of the Fusion of Graph Models and Point Net Model for Processing Graph and Point Cloud Data}{}{}{}{
% % Detailed achievements:%
% \begin{itemize}
% \item Supervisor: Prof. Javanmardi.
% \item Implementation and analysis of combining two common models in 3D Object classification, including SAG Pool and Point-Net, to gain the highest accuracy in point cloud classification.
% \end{itemize}}


% \vspace*{2em}

%------------------------------
% \vspace*{0.5em}
% \section{Language Proficiency}
% \cventry{October 2023}{TOEFL IBT Test: 84}{}{}{}{ 
% % Detailed achievements:%
% \begin{itemize}
% \item Reading: 23
% \item Listening: 23
% \item Speaking: 18
% \item Writing: 20
% \end{itemize}}

\vspace*{1em}

\begin{center}
References, further information, and proofs are available upon request
\end{center}

\end{document}
