\documentclass[11pt,a4paper,sans]{moderncv}
% Possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape'), and font family ('sans' and 'roman')

%----------------------------------------------------------------------------------------
% COLORS
%----------------------------------------------------------------------
\usepackage{xcolor}
% \usepackage{titlesec}/
% Main color
% \definecolor{maincol}{RGB}{255,150,0}
% \titlespacing{\section}{0pt}{\parskip}{-\parskip}
% Secondary colors
% \definecolor{secondcol}{RGB}{0,178,255}
\definecolor{thirdcol}{HTML}{3873B2}
% \definecolor{fourthcol}{RGB}{0,100,160}
% \definecolor{fifthcol}{RGB}{0,120,200}
% \definecolor{sixthcol}{RGB}{0,80,130}
\definecolor{color1}{HTML}{3873B2}
% Background color
% \definecolor{bgcol}{RGB}{255,255,255}

% Text color
% \definecolor{textcol}{RGB}{0,50,80}

% Section color
% \definecolor{sectcol}{RGB}{56,115,178}

\usepackage{mathpazo}
\usepackage{tikz}
\usetikzlibrary{arrows}

% Moderncv themes
\moderncvstyle{banking} % Style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % Color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', and 'black'
%\renewcommand{\familydefault}{\sfdefault} % To set the default font; use '\sfdefault' for the default sans-serif font, '\rmdefault' for the default roman one, or any TeX font name
\nopagenumbers{} % Uncomment to suppress automatic page numbering for CVs longer than one page

% Character encoding
\usepackage[utf8]{inputenc}
\usepackage{pdfpages}

% If you are not using xelatex or lualatex, replace with the encoding you are using
%\usepackage{CJKutf8} % If you need to use CJK to typeset your resume in Chinese, Japanese, or Korean
\usepackage{multicol}

% Adjust the page margins
\usepackage[scale=0.8,top=0.5cm,bottom=0.1cm]{geometry}
% \usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm} % If you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. Be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage{xpatch}
\xpatchcmd\cventry{,}{}{}{}
\makeatletter
\xpatchcmd\makehead
   {\titlestyle{~|~\@title}}%
   {\newline\newline\titlestyle{\@title}
   }%
   {}{}
\makeatother
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=thirdcol,
}


\vspace{7mm}
% Personal data

\name{}{\hspace{10mm}\textcolor{black}{Mohammad Choupan}}
\title{Front-End Developer} % Optional, remove/comment the line if not wanted

% \name{\textcolor{black}{Mohammad}}{\textcolor{black}{Choupan}}


% \address{70 Absolute Ave.}{L4Z 0A4 Mississauga}{Canada} % Optional, remove/comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
% \vspace*{7mm}
% \address % \address{pariyamd.github.io}
\phone[mobile]{+39 3520 119 670}
% \title{\normalfont}
% Optional, remove/comment the line if not wanted
% \phone[fixed]{+2~(345)~678~901} % Optional, remove/comment the line if not wanted
% \phone[fax]{+3~(456)~789~012} % Optional, remove/comment the line if not wanted
\email{mohamadchoupan80@gmail.com}
% Optional, remove/comment the line if not needed
\social[github]{mohamadch91}
% \social[linkedin]{mohammad-choupan-629959245}
% \photo[80pt][0.1pt]{pariya.png} % \date{2000-07-18}
%----------------------------------------------------------------------------------
% Content
%----------------------------------------------------------------------------------

\begin{document}
% \vspace {0mm}
\makecvtitle

\vspace {-2em}

\section{Profile}
\vspace{-1mm}
MSc student in Artificial Intelligence at the University of Bologna and Front-End Developer with 5+ years of experience building modern web interfaces. Specializing in React/Next.js, TypeScript, and responsive UI development, with a focus on performance, usability, and scalable component systems. Experienced in Agile teams and fast-paced environments.
%------------------------------

 % \setlength{\tabcolsep}{1pt}.
% \section{Research Interests}
% \vspace{-4mm}
% \begin{multicols}{3}
%     \begin{itemize}
%     \item Computer Vision
%     \item Panoptic Segmentation
%     \item Point Cloud Classification
% \vspace{-4mm}
    
%     \end{itemize}
% \vspace{-4mm}
    
% \end{multicols}


\section{Technical Skills}
\begin{itemize}
    \item \textbf{Languages:} JavaScript (ES6+), TypeScript, HTML5, CSS3, SQL
    \item \textbf{Front-End:} React, Next.js, React Native, Amazon Cloudscape, Redux Toolkit
    \item \textbf{Testing/Tooling:} Jest, React Testing Library, Vite/Webpack, ESLint, Prettier
    \item \textbf{GitOps / DevOps:} Git, GitLab CI/CD, GitHub Actions, Docker, Kubernetes, Helm
\end{itemize}




\section{Work Experience}
\vspace{1mm}

\cventry{2025 -- 2026}{Front-End Team Lead}{Goldiran Asayesh}{Tehran, Iran}{}{
    \vspace{1mm}
Goldiran Asayesh is an insurance provider for home appliances in Iran, with three product managers and field technicians handling repair and sales operations.
\begin{itemize}
\item Led a team of 3 front-end developers to launch a new customer-facing website and manage \textbf{4} products: \href{https://goldiranasayesh.com/}{Goldiran Asayesh}, \href{https://tech.kardoon.ir/}{Kardoon}, \href{https://inzi.ir/}{Inzi}, and \href{https://nexoland.ir}{Nexoland}.
\item Directed front-end execution end-to-end: requirements refinement, UI/component architecture, code reviews, sprint planning, and cross-functional coordination with product and back-end teams.
\item Move from manual builds to GitLab CI/CD (GitOps), making builds \textbf{2$\times$ faster} and cutting final bundle size by \textbf{40\%}; used Docker-based deployments and web-server operations to stabilize releases.
\end{itemize}}
\vspace{1mm}

\cventry{2024 -- 2025}{Front-End Developer}{OpenSecurity (OpenGovern)}{Remote}{}{
    \vspace{1mm}
OpenSecurity (OpenGovern) is a US-based \textbf{open-source} startup building a compliance and security platform for containerized and cloud environments, with dashboards to detect, track, and remediate compliance issues. \href{https://github.com/opengovern/}{GitHub}
\begin{itemize}
\item Participated in front-end delivery and release workflows for the open-source platform, collaborating with distributed engineers across time zones.
\item Expanded and maintained a production dashboard UI using Amazon Cloudscape; integrated back-end APIs and rolled out new compliance views.
\item Increased client-side loading speed by \textbf{60\% per request} by replacing the base library and optimizing the request/response handling flow.
\item Applied Kubernetes packaging via a Helm chart and enforced CI/CD release automation; reduced installation time to under 2 minutes and strengthened setup reliability.
\item Enhanced Steampipe usability by enabling offline SQL querying on cached datasets (500+ tables), boosting productivity in restricted-network environments.
\item Drove the delivery of 15+ integrations/plugins and corresponding “describers” across GitHub, Kubernetes, and major cloud providers (AWS, Azure, GCP, Linode).
\item Helped ship an \textbf{open-source} release that reached 600+ GitHub stars.
\end{itemize}}
\vspace{1mm}
\cventry{2024 -- 2024}{Front-End Developer (Freelance Project)}{Baham Store}{Tehran, Iran}{}{
\href{https://bahamstore.ir}{Website}
\begin{itemize}
    \item Created the entire e-commerce front end from scratch, defining page structure, routing, and reusable UI patterns for long-term maintainability.
    \item Applied core storefront flows: catalog/search, product pages, cart/checkout, user accounts, and order tracking with a responsive, mobile-first UI.
    \item Increased sales by \textbf{40\%} in normal periods and achieved \textbf{2$\times$} sales during Black Friday campaigns by optimizing product discovery and checkout UX.
\end{itemize}}

\newpage
\clearpage

\cventry{2023 -- 2024}{INVGAP (Inventory \& Gap Analysis)}{World Health Organization (WHO)}{Remote}{}{
    \vspace{1mm}
INVGAP is a WHO program for monitoring vaccine inventory and identifying supply gaps across multiple countries. The platform models \textbf{40+ database tables} and renders a complex hierarchical (tree) UI, requiring fast handling of \textbf{JSON payloads $>$1\,MB}. \href{https://aze.invgap.org}{Inventory Gap Analysis System}
\begin{itemize}
\item Designed and maintained the web front end using React.js and TypeScript, including data-heavy dashboards and role-based workflows.
\item Released a React Native mobile app to the App Store: \href{https://apps.apple.com/de/app/inventory-and-gap-analysis/id6447693397}{Inventory and Gap Analysis}.
\item Planned and validated analysis workflows across \textbf{26+ countries}, ensuring consistent UX and reporting outputs for stakeholders.
\item Coordinated production readiness for high-traffic usage with \textbf{1000+ concurrent users}, aligning with infrastructure teams on scaling measures (e.g., load balancing).
\end{itemize}}


\cventry{2021 -- 2023}{Front-End Developer (Freelance)}{Freelancer}{Tehran, Iran}{}{
\begin{itemize}   
    \item \textbf{POD App (petroleum marketplace).} \href{https://pod-app.com}{Website}
    \begin{itemize}
        \item Built the customer-facing web application and admin panel from scratch, establishing a scalable component architecture and shared UI modules.
        \item Executed marketplace and back-office flows: listings/search, product detail views, request/order creation, user management, and admin operations.
        \item Applied API integration patterns (REST), error handling, and state management to keep data-heavy screens consistent and reliable during iterative releases.
    \end{itemize}
    \vspace{1mm}
    \item \textbf{LandoLet (rental platform).}
    \begin{itemize}
        \item Participated in product execution for a UK apartment rental platform, translating product requirements into clear user flows and screen-level UI specifications.
        \item Created responsive UI screens aligned with design constraints and usability needs (search, listing details, and booking/contact flows).
        \item Coordinated with stakeholders to refine edge cases and acceptance criteria, ensuring predictable behavior across common user journeys.
        % Strict front-end resume: keep back-end line removed/commented.
    \end{itemize}
    \vspace{1mm}
    \item \textbf{Cloud Drive (internal tool).}
    \begin{itemize}
        \item Created a lightweight internal cloud-drive web app from scratch for company use, covering layout, navigation, and access-oriented UX.
        \item Implemented essential file workflows: upload, browsing, folder navigation, and basic permission-aware actions.
        \item Applied clean UI patterns to keep the tool simple for non-technical users and easy to extend with additional features.
    \end{itemize}
\end{itemize}}
%------------------------------
% \vspace*{0mm}
% \section{Teaching Assistant Experience}
% \cventry{Fall 2024}{Computer Networks}{Prof. Babak Sadeghian}{}{}{}
% \cventry{Fall 2023}{Cloud Computing}{Prof. Seyyed Ahmad Javadi}{}{}{}
% \cventry{Fall 2023}{Data Mining}{Prof. Maryam Mazlaghani}{}{}{}
% \cventry{Spring 2023}{Fundamentals of Robotics}{Prof. Mahdi Javanmardi}{}{}{}
% \cventry{Spring 2023}{Head TA Embedded and Real-time Systems}{Prof. Hamed Farbeh}{}{}{}
% \cventry{Spring 2023}{Algorithm Design}{Prof. Sajjad Shirali Shahreza}{}{}{}
% \cventry{Fall 2022}{Algorithm Design}{Prof. Mahdi Javanmardi}{}{}{}
% \cventry{Fall 2022}{Head TA Microprocessor and Assembly Lab}{Prof. Hamed Farbeh}{}{}{}
% \cventry{Spring 2022}{Head TA Algorithm Design}{Prof. Alireza Bagheri \& Prof. Sajjad Shirali Shahreza }{}{}{}
% \cventry{Spring 2022}{Microprocessor and Assembly}{Prof. Hamed Farbeh}{}{}{}
% \cventry{Fall 2021}{Data Structures and Algorithms}{Prof. Alireza Bagheri}{}{}{}
% \cventry{Fall 2021}{Fundamentals of Programming (C programming)}{Prof. Hossein Zeinali}{}{}{}

% --------------------------

% \clearpage
% \medskip
% % ------------------------
% \vspace*{3em}
% \section{Publications}

% \cventry{July 2022}{}{}{}{}{
% % Detailed achievements:%
% \vspace*{-2em}
% \begin{itemize}
% \item 
% M. Ebadpour, M. Javan, \textbf{M. Choupan}, M. Atyabi, "PointNet meets Self-Attention Graph Pooling: A Synergistic Approach to Point Cloud Classification," \textit{(in progress)}. Visit \href{https://github.com/MohsenEbadpour/PointNet-meets-Self-Attention-Graph-Pooling-A-Synergistic-Approach-to-Point-Cloud-Classification}{link}.
% \end{itemize}}

% \vspace*{-0.5em}
%
% \section{Achievements}
% \cventry{September 2019 - May 2024}{University Courses}{}{}{}{ 
% % Detailed achievements:%
% \begin{itemize}
% \item Completed Computer Engineering courses with an A+ score, totaling 143 credits, while working in reputable companies and conducting research alongside my studies.
% \end{itemize}} 

% \cventry{August 2018}{Ranked within the top 0.5\% (900 among 164,278 students) in the Iranian University Entrance Exam}{}{}{}{ 
% % Detailed achievements:%
% \begin{itemize}
% \item The exam is highly competitive as it is the only way to gain admission to universities in Iran.
% \end{itemize}}

% \cventry{September 2018}{National Chemistry Olympiad Bronze Medal}{}{}{}{
% % Detailed achievements:%
% \begin{itemize}
% \item Earning a medal in the Chemistry Olympiad is challenging, with only 30 people awarded medals in the entire country.
% \end{itemize}}
% % --------------------------------------------

% \section{Notable Projects}

% \cventry{Spring 2023}{Data Mining Course Projects}{\href{https://github.com/mohamadch91/Data-Mining-course}{GitHub}}{}{}{
% % Detailed achievements:%
% \begin{itemize}
% \item Preprocessed raw data and performed dimension reduction with PCA using a given dataset.
% \item Implemented a TensorFlow Neural Network project, tuned hyperparameters, and analyzed results using visualization.
% \item Applied association rules to a hypermarket dataset.
% \end{itemize}}

% \cventry{Spring 2022}{Search Engine}{\href{https://github.com/mohamadch91/AUT-Information-Retrieval}{GitHub}}{}{}{
% % Detailed achievements:%
% \begin{itemize}
% \item Built a news search engine that retrieves news articles by implementing tf-idf and k-means models and a k-nearest neighbors (KNN) classifier for categorizing unlabeled data in Python.
% \end{itemize}}

% \cventry{Fall 2021}{Fuzzy Inverted Pendulum}{\href{https://github.com/mohamadch91/Inverted-pendulum-FUZZY-control}{GitHub}}{}{}{
% % Detailed achievements:%
% \begin{itemize}
% \item This project consists of an inverted pendulum simulator and a fuzzy controller. The main goal was to develop a simple yet useful simulator to model the environment, allowing for the creation of a fuzzy controller for the inverted pendulum problem. It was implemented using pygame and pyfuzzy in Python 2.7.
% \end{itemize}}

% \cventry{Fall 2021}{Image Processing with ANN}{\href{https://github.com/mohamadch91/Image-processing-Neural-network}{GitHub}}{}{}{
% % Detailed achievements:%
% \begin{itemize}
% \item This is a simple example of image processing with ANN. The goal is to classify images of fruits using the Fruits-360 dataset. The project involved calculating the accuracy of the model.
% \end{itemize}}

% \cventry{Fall 2021}{Snail Jumper}{\href{https://github.com/mohamadch91/SnailJumper}{GitHub}}{}{}{
% % Detailed achievements:%
% \begin{itemize}
% \item This is a simple example of using neuroevolution in games. It uses neural networks and a genetic algorithm to control a snake.
% \end{itemize}}





\section{Education}

\cventry{2025 -- Present}{MSc in Artificial Intelligence}{University of Bologna, Italy}{}{}{
\begin{itemize}
    \item GPA: 30/30
\end{itemize}}

\cventry{2020 -- 2024}{Bachelor's Degree}{Amirkabir University of Technology, Tehran, Iran}{Computer Engineering}{}{\begin{itemize}
    \item GPA: 3.7/4
    \item GPA Over the Last Two Years: 3.83/4
\end{itemize}}

% \cventry{2016 -- 2019}{Diploma}{Atomic Energy High School, Tehran, Iran}{Mathematics and Physics Discipline}{}{}
% \vspace*{0.5em}
% \section{BSc Thesis}

% \cventry{August 2023 - June 2024}{Assessment of the Fusion of Graph Models and Point Net Model for Processing Graph and Point Cloud Data}{}{}{}{
% % Detailed achievements:%
% \begin{itemize}
% \item Supervisor: Prof. Javanmardi.
% \item Implementation and analysis of combining two common models in 3D Object classification, including SAG Pool and Point-Net, to gain the highest accuracy in point cloud classification.
% \end{itemize}}


% \vspace*{2em}

%------------------------------
% \vspace*{0.5em}
% \section{Language Proficiency}
% \cventry{October 2023}{TOEFL IBT Test: 84}{}{}{}{ 
% % Detailed achievements:%
% \begin{itemize}
% \item Reading: 23
% \item Listening: 23
% \item Speaking: 18
% \item Writing: 20
% \end{itemize}}

\vspace*{1em}

\begin{center}
References, further information, and proofs are available upon request
\end{center}

\end{document}
