\documentclass[11pt,a4paper,sans]{moderncv}
% Possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape'), and font family ('sans' and 'roman')

%----------------------------------------------------------------------------------------
% COLORS
%----------------------------------------------------------------------
\usepackage{xcolor}
% \usepackage{titlesec}/
% Main color
% \definecolor{maincol}{RGB}{255,150,0}
% \titlespacing{\section}{0pt}{\parskip}{-\parskip}
% Secondary colors
% \definecolor{secondcol}{RGB}{0,178,255}
\definecolor{thirdcol}{HTML}{3873B2}
% \definecolor{fourthcol}{RGB}{0,100,160}
% \definecolor{fifthcol}{RGB}{0,120,200}
% \definecolor{sixthcol}{RGB}{0,80,130}
\definecolor{color1}{HTML}{3873B2}
% Background color
% \definecolor{bgcol}{RGB}{255,255,255}

% Text color
% \definecolor{textcol}{RGB}{0,50,80}

% Section color
% \definecolor{sectcol}{RGB}{56,115,178}

\usepackage{mathpazo}
\usepackage{tikz}
\usetikzlibrary{arrows}

% Moderncv themes
\moderncvstyle{banking} % Style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % Color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', and 'black'
%\renewcommand{\familydefault}{\sfdefault} % To set the default font; use '\sfdefault' for the default sans-serif font, '\rmdefault' for the default roman one, or any TeX font name
\nopagenumbers{} % Uncomment to suppress automatic page numbering for CVs longer than one page

% Character encoding
\usepackage[utf8]{inputenc}
\usepackage{pdfpages}

% If you are not using xelatex or lualatex, replace with the encoding you are using
%\usepackage{CJKutf8} % If you need to use CJK to typeset your resume in Chinese, Japanese, or Korean
\usepackage{multicol}

% Adjust the page margins
\usepackage[scale=0.8,top=0.5cm,bottom=0.1cm]{geometry}
% \usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm} % If you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. Be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage{xpatch}
\xpatchcmd\cventry{,}{}{}{}
\makeatletter
\xpatchcmd\makehead
   {\titlestyle{~|~\@title}}%
   {\newline\newline\titlestyle{\@title}
   }%
   {}{}
\makeatother
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=thirdcol,
}


\vspace{7mm}
% Personal data

\name{}{\hspace{10mm}\textcolor{black}{Mohammad Choupan}}
\title{Back-End Developer} % Optional, remove/comment the line if not wanted

% \name{\textcolor{black}{Mohammad}}{\textcolor{black}{Choupan}}


% \address{70 Absolute Ave.}{L4Z 0A4 Mississauga}{Canada} % Optional, remove/comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
% \vspace*{7mm}
% \address % \address{pariyamd.github.io}
\phone[mobile]{+39 3520 119 670}
% \title{\normalfont}
% Optional, remove/comment the line if not wanted
% \phone[fixed]{+2~(345)~678~901} % Optional, remove/comment the line if not wanted
% \phone[fax]{+3~(456)~789~012} % Optional, remove/comment the line if not wanted
\email{mohamadchoupan80@gmail.com}
\homepage{mohamadch91.github.io}
% Optional, remove/comment the line if not needed
\social[github]{mohamadch91}
% \social[linkedin]{mohammad-choupan-629959245}
% \photo[80pt][0.1pt]{pariya.png} % \date{2000-07-18}
%----------------------------------------------------------------------------------
% Content
%----------------------------------------------------------------------------------

\begin{document}
% \vspace {0mm}
\makecvtitle

\vspace {-2em}

\section{Profile}
\vspace{-1mm}
MSc student in Artificial Intelligence at the University of Bologna and Back-End Developer with 5+ years of experience building and operating web applications. Specializing in Python and Django, with a focus on scalable APIs, database design, and production-ready back-end systems. Experienced in Agile teams and fast-paced environments.
%------------------------------

 % \setlength{\tabcolsep}{1pt}.
% \section{Research Interests}
% \vspace{-4mm}
% \begin{multicols}{3}
%     \begin{itemize}
%     \item Computer Vision
%     \item Panoptic Segmentation
%     \item Point Cloud Classification
% \vspace{-4mm}
    
%     \end{itemize}
% \vspace{-4mm}
    
% \end{multicols}


\section{Technical Skills}
\begin{itemize}
    \item \textbf{Languages:} Python, SQL, Bash
    \item \textbf{Back-End:} Django, Django REST Framework (DRF), REST APIs
    \item \textbf{Microservices \& Messaging:} gRPC (service-to-service), Celery, RabbitMQ
    \item \textbf{Databases \& Caching:} PostgreSQL, MySQL, Redis
    \item \textbf{Testing/Tooling:} Pytest, Django Test Framework, Postman, Swagger/OpenAPI
    \item \textbf{GitOps / DevOps:} Git, GitLab CI/CD, GitHub Actions, Docker, Kubernetes, Helm
\end{itemize}




\section{Work Experience}
\vspace{1mm}

\cventry{2025 -- 2026}{DevOps Engineer}{Goldiran Asayesh}{}{}{
\vspace{1mm}
Goldiran Asayesh is an insurance provider for home appliances in Iran, with three product managers and field technicians handling repair and sales operations.
\begin{itemize}
\item Owned CI/CD and production operations for \textbf{4} products: \href{https://goldiranasayesh.com/}{Goldiran Asayesh}, \href{https://tech.kardoon.ir/}{Kardoon}, \href{https://inzi.ir/}{Inzi}, and \href{https://nexoland.ir}{Nexoland}.
\item Migrated from manual builds to automated Jenkins pipelines (GitOps), making builds \textbf{2$\times$ faster} and reducing final build artifacts by \textbf{40\%}.
\item Executed Docker-based build and deployment workflows via Jenkins, including environment configuration, release automation, and rollback readiness.
\item Set up centralized logging with Elasticsearch for log aggregation and search; decreased time-to-debug by \textbf{2$\times$} (per team lead feedback).
\item Applied monitoring and alerting with Prometheus and Grafana to increase service visibility and accelerate operational response.
\end{itemize}}
\vspace{1mm}

\vspace{1mm}
\cventry{2024 -- 2025}{Back-End Developer}{OpenSecurity (OpenGovern)}{Remote}{}{
\vspace{1mm}
OpenSecurity (OpenGovern) is a US-based \textbf{open-source} startup building a compliance and security platform for containerized and cloud environments, with dashboards to detect, track, and remediate compliance issues. \href{https://github.com/opengovern/}{GitHub}
\begin{itemize}
\item Built and maintained back-end services in Python, collaborating with distributed engineers across time zones and contributing to release workflows.
\item Created a Python package to run and manage an AI/LLM pipeline (prompt orchestration, tool/connector execution, and structured outputs) to support product automation use cases.
\item Amplified request performance by \textbf{60\%} by replacing a core base library and optimizing the request/response path.
\item Applied Kubernetes packaging via a Helm chart and enforced CI/CD release automation; reduced installation time to under 2 minutes and strengthened setup reliability.
\item Enhanced Steampipe usability by enabling offline SQL querying on cached datasets (500+ tables), expanding functionality for restricted-network environments.
\item Led delivery of 15+ integrations/plugins and corresponding “describers” across GitHub, Kubernetes, and major cloud providers (AWS, Azure, GCP, Linode).
\item Helped ship an \textbf{open-source} release that reached 600+ GitHub stars.
\end{itemize}}
\vspace{1mm}

\cventry{2024 -- 2024}{Back-End Developer (Freelance Project)}{Baham Store}{}{}{
\href{https://bahamstore.ir}{Website}
\begin{itemize}
    \item Built the back end from scratch using Python/Django, defining the data model, API structure, and admin workflows for an e-commerce platform.
    \item Managed a catalog of \textbf{10K+ products} using Celery for asynchronous jobs (imports/updates, notifications, background processing) and caching to reduce database load.
    \item Increased sales by \textbf{40\%} in normal periods and achieved \textbf{2$\times$} sales during Black Friday campaigns by optimizing back-end performance and checkout reliability.
\end{itemize}}

\newpage
\clearpage

\cventry{2023 -- 2024}{Back-End Developer}{INVGAP (Inventory \& Gap Analysis), World Health Organization (WHO)}{Remote}{}{
\vspace{1mm}
INVGAP is a WHO program for monitoring vaccine inventory and identifying supply gaps across multiple countries. \href{https://aze.invgap.org}{Inventory Gap Analysis System}
\begin{itemize}
\item Developed the back-end data model with \textbf{40+ database tables}, defining relationships and constraints to support complex inventory and gap-analysis workflows.
\item Built and maintained high-throughput APIs and database transaction flows to support \textbf{1000+ concurrent users} in production.
\item Processed large data imports, including \textbf{Excel files up to 30\,MB}, applying validation, batching, and safe transaction handling to protect data integrity and performance.
\item Coordinated deployment readiness with infrastructure teams (e.g., load balancing and scaling), ensuring reliability across \textbf{26+ countries}.
\end{itemize}}
\cventry{2021 -- 2023}{Back-End Developer (Freelance)}{Freelancer}{}{}{
\begin{itemize}
    \item \textbf{POD App (petroleum marketplace).} \href{https://pod-app.com}{Website}
    \begin{itemize}
        \item Built back-end services with Python/Django, defining domain models and transactional workflows for listings, requests/orders, and admin operations.
        \item Applied \textbf{gRPC} for microservice-to-microservice communication to keep internal integrations fast and strongly typed.
        \item Ran asynchronous processing through \textbf{RabbitMQ} middleware with \textbf{Celery} workers for queues (background jobs, notifications, scheduled tasks), improving reliability under load.
    \end{itemize}
    \vspace{1mm}
    \item \textbf{LandoLet (rental platform).}
    \begin{itemize}
        \item Built and maintained Python/Django APIs for search, listing details, booking/contact requests, and user account workflows.
        \item Designed relational data models and enforced authentication/authorization to secure user and listing operations.
        \item Applied structured logging, error handling, and systematized tests to keep releases predictable.
    \end{itemize}
    \vspace{1mm}
    \item \textbf{Cloud Drive (internal tool).}
    \begin{itemize}
        \item Built a Django-based file service to support large uploads, storage, and access-controlled downloads for internal users.
        \item Applied scalable upload handling (chunked uploads, server-side validation, and background processing) to reduce timeouts and protect data integrity.
        \item Added caching and indexed queries for fast file browsing and metadata retrieval.
    \end{itemize}
\end{itemize}}





\section{Education}

\cventry{2025 -- Present}{MSc in Artificial Intelligence}{University of Bologna, Italy}{}{}{
\begin{itemize}
    \item GPA: 30/30
\end{itemize}}

\cventry{2020 -- 2024}{Bachelor's Degree}{Amirkabir University of Technology, }{Computer Engineering}{}{\begin{itemize}
    \item GPA: 3.7/4
    \item GPA Over the Last Two Years: 3.83/4
\end{itemize}}



\vspace*{1em}

\begin{center}
References, further information, and proofs are available upon request
\end{center}

\end{document}
