\documentclass[11pt,a4paper,sans]{moderncv}
% Possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape'), and font family ('sans' and 'roman')

%----------------------------------------------------------------------------------------
% COLORS
%----------------------------------------------------------------------
\usepackage{xcolor}
% \usepackage{titlesec}/
% Main color
\definecolor{maincol}{RGB}{255,150,0}
% \titlespacing{\section}{0pt}{\parskip}{-\parskip}
% Secondary colors
\definecolor{secondcol}{RGB}{0,178,255}
\definecolor{thirdcol}{RGB}{50,120,169}
\definecolor{fourthcol}{RGB}{0,100,160}
\definecolor{fifthcol}{RGB}{0,120,200}
\definecolor{sixthcol}{RGB}{0,80,130}

% Background color
\definecolor{bgcol}{RGB}{255,255,255}

% Text color
\definecolor{textcol}{RGB}{0,50,80}

% Section color
\definecolor{sectcol}{RGB}{255,255,255}

\usepackage{mathpazo}
\usepackage{tikz}
\usetikzlibrary{arrows}

% Moderncv themes
\moderncvstyle{classic} % Style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % Color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', and 'black'
%\renewcommand{\familydefault}{\sfdefault} % To set the default font; use '\sfdefault' for the default sans-serif font, '\rmdefault' for the default roman one, or any TeX font name
\nopagenumbers{} % Uncomment to suppress automatic page numbering for CVs longer than one page

% Character encoding
\usepackage[utf8]{inputenc}
\usepackage{pdfpages}

% If you are not using xelatex or lualatex, replace with the encoding you are using
%\usepackage{CJKutf8} % If you need to use CJK to typeset your resume in Chinese, Japanese, or Korean
\usepackage{multicol}

% Adjust the page margins
\usepackage[scale=0.8,top=0.5cm,bottom=0.1cm]{geometry}
% \usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm} % If you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. Be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage{xpatch}
\xpatchcmd\cventry{,}{}{}{}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=thirdcol,
}


\vspace{7mm}
% Personal data
\name{Mohammad}{Choupan}
% \address{70 Absolute Ave.}{L4Z 0A4 Mississauga}{Canada} % Optional, remove/comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\vspace*{7mm}
% \address % \address{pariyamd.github.io}
\phone[mobile]{+989126196168}
\title{\normalfont}
% Optional, remove/comment the line if not wanted
% \phone[fixed]{+2~(345)~678~901} % Optional, remove/comment the line if not wanted
% \phone[fax]{+3~(456)~789~012} % Optional, remove/comment the line if not wanted
\email{mohamadchoupan80@gmail.com}
% Optional, remove/comment the line if not needed
\social[github]{mohamadch91}
% \photo[80pt][0.1pt]{pariya.png} % \date{2000-07-18}
%----------------------------------------------------------------------------------
% Content
%----------------------------------------------------------------------------------

\begin{document}
% \vspace {0mm}
\makecvtitle

\vspace {-2em}

\section{Profile}
\vspace{-1mm}
Graduated from Amirkabir University of Technology with a degree in Computer Engineering. Full-stack developer with over 5 years of experience, skilled at building web applications from the ground up. Proficient in agile methodologies and comfortable working in fast-paced environments.
%------------------------------

 % \setlength{\tabcolsep}{1pt}.
% \section{Research Interests}
% \vspace{-4mm}
% \begin{multicols}{3}
%     \begin{itemize}
%     \item Computer Vision
%     \item Panoptic Segmentation
%     \item Point Cloud Classification
% \vspace{-4mm}
    
%     \end{itemize}
% \vspace{-4mm}
    
% \end{multicols}
\section{Work Experience}
\vspace{-1mm}

\cventry{July 2025 -- March 2025}{AI Engineer}{Behavior Understanding}{Tehran, Iran}{}{
\begin{itemize}
\item Designed a large language model (LLM) to analyze government behavior based on their activity across social networks and news sources.
\end{itemize}}

\cventry{July 2025 -- March 2025}{AI Engineer}{Profile Mapping}{Tehran, Iran}{}{
\begin{itemize}
\item Mapped different social media profiles belonging to the same individual and extracted comprehensive personal data.
\end{itemize}}






\cventry{November 2024 -- March 2025}{Software Engineer}{Opensecurity}{Remote}{}{
\begin{itemize}
\item Opensecurity was a US-based startup. I worked as a full-stack software engineer, designing and developing various components of the platform. \href{https://github.com/opengovern/}{Repo}
  \begin{enumerate}
        \item[-] Developed a chatbot to generate SQL queries from natural language in under 5 seconds.
        \item[-] Built a web UI based on Amazon Cloudscape.
        \item[-] Packaged the platform as a Helm chart for modular, production-ready Kubernetes deployment, reducing installation time to under 2 minutes.
        \item[-] Enhanced Steampipe to support offline SQL querying on cached data with 500+ tables.
        \item[-] Led the development of 15+ plugins and their corresponding "describers" for GitHub, Kubernetes, AWS, Azure, GCP, and Linode.
        \item[-] Published an open-source tool with 600+ stars on GitHub.
    \end{enumerate}
\end{itemize}}



\cventry{March 2024 -- November 2024}{Front-end Team Lead}{Goldiran asayesh}{Tehran, Iran}{}{
\begin{itemize} % 3 months
\item Goldiran Asayesh is a company that provides insurance services. I am responsible for leading a team of three front-end developers to create a new website for the company and manage existing websites, such as \href{https://goldiranasayesh.com/}{Goldiran Asayesh},
                        \href{https://tech.kardoon.ir/}{Kardoon} and
                        \href{https://inzi.ir/}{Inzi}.
                        Additionally, I handled DevOps tasks, including writing CI/CD in gitlab, Docker, and web server management.
\end{itemize}}



\cventry{February 2021 -- Present}{Freelancing as a Full-stack Developer}{Tehran, Iran}{}{}{
\begin{itemize} % 3 months
    \item \textbf{Designed and developed the \href{https://aze.invgap.org}{Inventory Gap Analysis System} for World Help Organization (WHO).}
    \begin{enumerate}
         \item[-] Worked as a full-stack developer using ReactJS and Django.
        \item[-] Developed a mobile app \href{https://apps.apple.com/de/app/inventory-and-gap-analysis/id6447693397}{Inventory and Gap Analysis} with React Native, published on the App Store.
        \item[-] Designed and validated analysis workflows for vaccine stock data in over 13 countries, including Ukraine, Azerbaijan, the Philippines, and more.
        \item[-] Implemented load balancing to handle traffic for all countries on a single server.
    \end{enumerate}
    \item \textbf{Designed and developed Cloud Drive.}
    \begin{enumerate}
        \item[-] Designed a simple cloud drive for personal use by the company.
    \end{enumerate}
    \item \textbf{Designed and developed Baham store online shop website.}
    \begin{enumerate}
        \item[-] Designed a complicated shop for Baham store. Iran's biggest apple store.  \href{https://bahamstore.ir}{Website}
    \end{enumerate}
     \item \textbf{POD app}
    \begin{enumerate}
        \item[-] Pod App is a petroleum marketplace where users can buy and sell petroleum products. I am responsible for developing both the website and the admin Panel app for this project using ReactJS and Django. The app is currently still under development. \href{https://pod-app.com}{Website}
    \end{enumerate}
     \item \textbf{LandoLet}
    \begin{enumerate}
        \item[-] LandoLet is a mobile app for renting an apartment in uk, I’m using Django-DRF to develop
the back end of this mobile app \href{https://github.com/mohamadch91/LandoLet-app-backend}{repo}
    \end{enumerate}
\end{itemize}}

\cventry{April 2023 -- June 2024}{Point Cloud Classification}{Tehran, Iran}{}{}{
\begin{itemize} % 3 months
\item Finding the best way to classify point cloud data with the highest accuracy.
\end{itemize}}

\cventry{April 2023 -- June 2024}{Evaluation of positioning error in self-driving cars using map matching methods}{Tehran, Iran}{}{}{
\begin{itemize} % 3 months
\item Finding Object cause error in NDT matching algorithm.Use Neural Networks to find object can cause error and
objects can reduce the error.
\end{itemize}}

% \newpage


%------------------------------
% \vspace*{0mm}
% \section{Teaching Assistant Experience}
% \cventry{Fall 2024}{Computer Networks}{Prof. Babak Sadeghian}{}{}{}
% \cventry{Fall 2023}{Cloud Computing}{Prof. Seyyed Ahmad Javadi}{}{}{}
% \cventry{Fall 2023}{Data Mining}{Prof. Maryam Mazlaghani}{}{}{}
% \cventry{Spring 2023}{Fundamentals of Robotics}{Prof. Mahdi Javanmardi}{}{}{}
% \cventry{Spring 2023}{Head TA Embedded and Real-time Systems}{Prof. Hamed Farbeh}{}{}{}
% \cventry{Spring 2023}{Algorithm Design}{Prof. Sajjad Shirali Shahreza}{}{}{}
% \cventry{Fall 2022}{Algorithm Design}{Prof. Mahdi Javanmardi}{}{}{}
% \cventry{Fall 2022}{Head TA Microprocessor and Assembly Lab}{Prof. Hamed Farbeh}{}{}{}
% \cventry{Spring 2022}{Head TA Algorithm Design}{Prof. Alireza Bagheri \& Prof. Sajjad Shirali Shahreza }{}{}{}
% \cventry{Spring 2022}{Microprocessor and Assembly}{Prof. Hamed Farbeh}{}{}{}
% \cventry{Fall 2021}{Data Structures and Algorithms}{Prof. Alireza Bagheri}{}{}{}
% \cventry{Fall 2021}{Fundamentals of Programming (C programming)}{Prof. Hossein Zeinali}{}{}{}

% --------------------------

% \clearpage
% \medskip
% % ------------------------
% \vspace*{3em}
% \section{Publications}

% \cventry{July 2022}{}{}{}{}{
% % Detailed achievements:%
% \vspace*{-2em}
% \begin{itemize}
% \item 
% M. Ebadpour, M. Javan, \textbf{M. Choupan}, M. Atyabi, "PointNet meets Self-Attention Graph Pooling: A Synergistic Approach to Point Cloud Classification," \textit{(in progress)}. Visit \href{https://github.com/MohsenEbadpour/PointNet-meets-Self-Attention-Graph-Pooling-A-Synergistic-Approach-to-Point-Cloud-Classification}{link}.
% \end{itemize}}

% \vspace*{-0.5em}
%
% \section{Achievements}
% \cventry{September 2019 - May 2024}{University Courses}{}{}{}{ 
% % Detailed achievements:%
% \begin{itemize}
% \item Completed Computer Engineering courses with an A+ score, totaling 143 credits, while working in reputable companies and conducting research alongside my studies.
% \end{itemize}} 

% \cventry{August 2018}{Ranked within the top 0.5\% (900 among 164,278 students) in the Iranian University Entrance Exam}{}{}{}{ 
% % Detailed achievements:%
% \begin{itemize}
% \item The exam is highly competitive as it is the only way to gain admission to universities in Iran.
% \end{itemize}}

% \cventry{September 2018}{National Chemistry Olympiad Bronze Medal}{}{}{}{
% % Detailed achievements:%
% \begin{itemize}
% \item Earning a medal in the Chemistry Olympiad is challenging, with only 30 people awarded medals in the entire country.
% \end{itemize}}
% % --------------------------------------------
\clearpage
\section{Notable Projects}

\cventry{Spring 2023}{Data Mining Course Projects}{\href{https://github.com/mohamadch91/Data-Mining-course}{GitHub}}{}{}{
% Detailed achievements:%
\begin{itemize}
\item Preprocessed raw data and performed dimension reduction with PCA using a given dataset.
\item Implemented a TensorFlow Neural Network project, tuned hyperparameters, and analyzed results using visualization.
\item Applied association rules to a hypermarket dataset.
\end{itemize}}

\cventry{Spring 2022}{Search Engine}{\href{https://github.com/mohamadch91/AUT-Information-Retrieval}{GitHub}}{}{}{
% Detailed achievements:%
\begin{itemize}
\item Built a news search engine that retrieves news articles by implementing tf-idf and k-means models and a k-nearest neighbors (KNN) classifier for categorizing unlabeled data in Python.
\end{itemize}}

\cventry{Fall 2021}{Fuzzy Inverted Pendulum}{\href{https://github.com/mohamadch91/Inverted-pendulum-FUZZY-control}{GitHub}}{}{}{
% Detailed achievements:%
\begin{itemize}
\item This project consists of an inverted pendulum simulator and a fuzzy controller. The main goal was to develop a simple yet useful simulator to model the environment, allowing for the creation of a fuzzy controller for the inverted pendulum problem. It was implemented using pygame and pyfuzzy in Python 2.7.
\end{itemize}}

\cventry{Fall 2021}{Image Processing with ANN}{\href{https://github.com/mohamadch91/Image-processing-Neural-network}{GitHub}}{}{}{
% Detailed achievements:%
\begin{itemize}
\item This is a simple example of image processing with ANN. The goal is to classify images of fruits using the Fruits-360 dataset. The project involved calculating the accuracy of the model.
\end{itemize}}

\cventry{Fall 2021}{Snail Jumper}{\href{https://github.com/mohamadch91/SnailJumper}{GitHub}}{}{}{
% Detailed achievements:%
\begin{itemize}
\item This is a simple example of using neuroevolution in games. It uses neural networks and a genetic algorithm to control a snake.
\end{itemize}}


% \vspace*{-2em}
\section{Technical Skills}

\cventry{}{Programming Languages:}{Python, Bash, JavaScript}{}{}{
}
\vspace*{-1em}

\cventry{}{Tools/Frameworks:}{PyTorch, Scikit-Learn, TensorFlow, Pandas, NumPy, ReactJS, Django}{}{}{
}
\vspace*{-1em}

\cventry{}{Other:}{Git, LaTeX, Linux }{}{}{
}
\vspace*{-1em}


\section{Education}
\cventry{2020 -- 2024}{Bachelor's Degree}{Amirkabir University of Technology, Tehran, Iran}{Computer Engineering}{}{\begin{itemize}
    \item GPA: 3.7/4
    \item GPA Over the Last Two Years: 3.83/4
\end{itemize}}

% \cventry{2016 -- 2019}{Diploma}{Atomic Energy High School, Tehran, Iran}{Mathematics and Physics Discipline}{}{}
% \vspace*{0.5em}
\section{BSc Thesis}

\cventry{August 2023 - June 2024}{Assessment of the Fusion of Graph Models and Point Net Model for Processing Graph and Point Cloud Data}{}{}{}{
% Detailed achievements:%
\begin{itemize}
\item Supervisor: Prof. Javanmardi.
\item Implementation and analysis of combining two common models in 3D Object classification, including SAG Pool and Point-Net, to gain the highest accuracy in point cloud classification.
\end{itemize}}


% \vspace*{2em}

%------------------------------
% \vspace*{0.5em}
% \section{Language Proficiency}
% \cventry{October 2023}{TOEFL IBT Test: 84}{}{}{}{ 
% % Detailed achievements:%
% \begin{itemize}
% \item Reading: 23
% \item Listening: 23
% \item Speaking: 18
% \item Writing: 20
% \end{itemize}}

\vspace*{1em}

\begin{center}
References, further information, and proofs are available upon request
\end{center}

\end{document}
